---
title: "Weight of Fish"
author: "Matthew Ramirez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
```


### Best Models

```{r}
PerchModel1 <- lm(Weight~ .,data=Perch)
summary.lm(PerchModel1)
```


### Best Two regressor model

```{r}
library(leaps)
PerchModel1automate <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Perch <- summary(PerchModel1automate)
as.data.frame(summary.Perch$outmat)
library(car)
subsets(PerchModel1automate,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

After running this code, I found the best single element regression model (Height), the best 2 element regression models (Height and Width), and I was also able to get the best 3, 4 and 5 elements regression models. Statistically, how i judged the element regression models is by checking the adjusted R square values.

## Pike

```{r}
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
```


### Best Models

```{r}
PikeModel1 <- lm(Weight~ .,data=Pike)
summary.lm(PikeModel1) 
```

### Best Two regressor Models

```{r}
library(leaps)
PikeModel1automate <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Pike <- summary(PikeModel1automate)
as.data.frame(summary.Pike$outmat)
library(car)
subsets(PikeModel1automate,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

After running the code for the Pike, I was able to get that the best 2 regressor models were length 1 and Length 3. However, the best regressor models were Length 1, 2 and 3 along with the height and Width which is the complete model. All of the models were judged based on the adjusted R square values.

## Roach

```{r}
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
```

### Best Models

```{r}
RoachModel1 <- lm(Weight~ .,data=Roach)
summary.lm(RoachModel1) 
```

### Best Two regressor model

```{r}
library(leaps)
RoachModel1automate <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Roach <- summary(RoachModel1automate)
as.data.frame(summary.Roach$outmat)
library(car)
subsets(RoachModel1automate,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

After running this code, i found the single best element regression model (Height), the best 2 element regression models (Height and Width), and I was able to get 3,4 and 5 elements regression models, Statistically, how I judged the element regression models is by checking the adjusted R square values.

## Final Summary Statements

In this assignment, I was able to compare regressor models for different types of fishes. For each fish I estimated the weight factor and compared the regressor models using the adjusted R square models. For the Perch, the best 2 element models were height and width. For Pike, the best 2 models were length 1 and 3. however, the best regressor models and the best models were length 1, 2 and 3 along with height and width. Finally for the Roach, the best 2 regressor models and the best models in general were length 3 and width. All models were judged by checking the adjusted R square values.
